troubleshooting

### 2024-10-01 README.Rmd
0.99.1

You can install the stable release from Bioconductor:

Alternatively, you can install the development version from github.

```{r,eval = FALSE}
devtools::install_github("baynec2/mspms",
    ref = "develop"
)
```

>>>>

You can install the development version from github.

```{r,eval = FALSE}
devtools::install_github("baynec2/mspms")
```
